\documentclass[]{resume-openfont}

\pagestyle{fancy}
\resetHeaderAndFooter

%--------------------------------------------------------------
% Convenience command - make it easy to fill template

% Create job position command. Parameters: company, position, location, when
\newcommand{\resumeHeading}[4]{\runsubsection{\uppercase{#1}}\descript{ | #2}\hfill\location{#3 | #4}\fakeNewLine}

% Create education heading. Parameters: Name, degree, location, when
\newcommand{\educationHeading}[4]{\runsubsection{#1}\hspace*{\fill}  \location{#3 | #4}\\
\descript{#2}\fakeNewLine}

% Create project heading. Parameters: Name, link, Tech stack
\newcommand{\projectHeading}[3]{\Project{#1}{#2}
\descript{#3}\\}

\newcommand{\projectHeadingWithDate}[4]{\Project{#1}{#2}
\descript{#3 | #4}\\}

% Parameters: courses
\newcommand{\courseWork}[1]{\textbf{Coursework:} #1}

% Parameters: courses
\newcommand{\teacherAssistant}[1]{\textbf{Teacher Assistant (TA):} #1}
 
%--------------------------------------------------------------
\begin{document}

%--------------------------------------------------------------
%     Profile
%--------------------------------------------------------------
\newcommand{\yourName}{Ali Mohsin}
% How you want it to show up on the resume
\newcommand{\yourWebsite}{webiste}
% vs how you want it to show up. If it's the same you can just replace "\yourWebsiteLink" with "yourWebsite"
\newcommand{\yourWebsiteLink}{website}
\newcommand{\yourEmail}{ali.mohsin05@gmail.com}
\newcommand{\yourPhone}{1-571-233-5190}
\newcommand{\githubUserName}{Paritybitz}
\newcommand{\linkedInUserName}{in/alimohsin05}

% An alternate profile section 
% \alignProfileTable
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%     \ralewayBold{\href{\yourWebsiteLink}{\Large \yourName}} & 
%     Email : \href{mailto:\yourEmail}{\yourEmail}
%     \\
%     \href{https://github.com/\githubUserName}{GitHub://\githubUserName} & 
%     Mobile : \yourPhone
%     \\
%     \href{https://www.linkedin.com/in/\linkedInUserName}{LinkedIn://\linkedInUserName} & Website : \href{\yourWebsiteLink}{\yourWebsite}
%     \\
% \end{tabular*}

\begin{center}
    \Huge \scshape \latoRegular{\yourName} \\ \vspace{1pt}
    \small \href{mailto:\yourEmail}{\underline{\yourEmail}}  $|$  \yourPhone $|$ 
    \href{https://www.linkedin.com/in/\linkedInUserName}{\underline{linkedIn/\linkedInUserName}} $|$
    \href{https://github.com/\githubUserName}{\underline{github/\githubUserName}} 
    % $|$ \href{\yourWebsiteLink}{\underline{\yourWebsite}}
\end{center}

%--------------------------------------------------------------
%     Education
%--------------------------------------------------------------
\section{Education}
% Put school first and degree second if your school is reputable
\educationHeading{B.S, Applied Computer Science, \\ conc. Software Engineering, GPA: 3.6/4.0 (Dean’s List)}{George Mason University}{Fairfax, VA}{\textit{Expected Dec 2026}}

% \teacherAssistant{World Wide Web Information Systems Development}
\courseWork{(AP/DE Credits: 46) • Previous: Intro to CS (Python), Object-Oriented Programming (Python and Java), Statistics
• Current: Data Structures, Formal Methods/Models, Software Usability Analysis/Design, Low-level Prog (C)}
\sectionsep

%--------------------------------------------------------------
%     Experience
%--------------------------------------------------------------
\section{Work Experience}
\resumeHeading{FiveRivers Technologies}{Data Scientist Intern}{Lahore, Pakistan}{May 2024 – Aug 2024}
\begin{bullets}
    \item Designed and implemented a dashboard using \textbf{React} and \textbf{TypeScript} to visualize data stored in \textbf{DynamoDB}, decreasing time to understand delivery driver work sessions by over 10 times.
    %  \item Here is another bullet that I might choose to uncomment for some jobs
    \item Ensured only authorized employees have access to the application by creating an \textbf{AWS Lambda@Edge} function to intercept and sign valid requests.
    \item Devised and deployed the infrastructure in TypeScript through \textbf{AWS CDK}, then created efficient algorithms to process data from a custom \textbf{REST API}, so it could scale to handle millions of deliveries.
    \item Setup a CI/CD pipeline and exceeded requirements in each stage, which lead to the application being pushed to production.
\end{bullets}
\sectionsep


%--------------------------------------------------------------
%     Projects
%--------------------------------------------------------------
\section{Projects}

\projectHeading{Automated Spear-Phisher}{https://github.com/Aarif123456/Fb-Twitter-gui}{Python, PySpark, Selenium, Apache, NLP, Big Data}
A security research tool to send targeted spam messages on either Facebook or Twitter. The program analyzes the feed of its target to increase the effectiveness of the messages.\\
\sectionsep
  
\projectHeading{Image Repository}{https://github.com/Aarif123456/image\_repository}{Java, PHP, React, TypeScript, Maven, GCP, MySQL}
A full-stack image repository, where users can store their files. Created a GCP cloud function to implement \href{https://www.cs.utexas.edu/~bwaters/publications/papers/cp-abe.pdf}{CP-ABE} encryption and used it to ensure files are secure at rest.\\
\sectionsep

\projectHeading{Image Repository}{https://github.com/Aarif123456/image\_repository}{Java, PHP, React, TypeScript, Maven, GCP, MySQL}
A full-stack image repository, where users can store their files. Created a GCP cloud function to implement \href{https://www.cs.utexas.edu/~bwaters/publications/papers/cp-abe.pdf}{CP-ABE} encryption and used it to ensure files are secure at rest.\\
\sectionsep

% Example using bullets and dates 
% \projectHeadingWithDate{Hogwart\textquotesingle{}s Library Management System}{https://github.com/Aarif123456/hogwartslibrary}{PHP, JavaScript, HTML, CSS, MySQL}{Aug 2019}
% \begin{bullets}
    % \item A full-stack library management system, where users can manage books and holds on their accounts. Users can search the library\textquotesingle{}s catalogue, which has every book mentioned in the Harry Potter series. The system distinguishes between 4 users. For examples, librarians who can also check or return books on behalf of users.\\
% \end{bullets}
% \sectionsep

%--------------------------------------------------------------
%     Volunteer Initiatives
%--------------------------------------------------------------
\section{Volunteer Initiatives}
\resumeHeading{STEM Kids}{Lead Coach and Curriculum Creator}{Alexandria, VA}{June 2021 – Current}
\begin{bullets}
    \item Designed an engaging STEM curriculum to inspire kids aged 9-15 to explore robotics and programming.
Introduced programming tools including Scratch, Lego Mindstorms, and Python.
    %  \item Here is another bullet that I might choose to uncomment for some jobs
    \item Developed and instructed a course to enhance public speaking and presentation design skills,
emphasizing effective communication and leadership abilities.
\end{bullets}
\sectionsep

%--------------------------------------------------------------
%     Skills
%--------------------------------------------------------------
\section{Skills}
\begin{skillList}
    \singleItem{Languages:}{Java, C++, Python, C\#, PHP, Prolog, Bash, C, Racket, SQL}
    \\
    \singleItem{Web Development:}{React, JavaScript, TypeScript, HTML/CSS}
    \\
    \singleItem{Technology:}{Git, AWS, GCP, Azure, Docker, Unity, Apache, \LaTeX, MongoDB, DynamoDB, Neo4j}
\end{skillList}

\sectionsep

\section{Interests/Activities}
\begin{skillList}
    \singleItem{\textbf{Interests:}}{Soccer, Weightlifting, Running, MMA, Photography (Instagram: art0grafy), Stock Trading}
    \\
    \singleItem{\textbf{Activities:}}{Travel Soccer Coach, Soccer Referee, Substitute Teacher, Athletic Trainer, Calculus Tutor}
    \\
\end{skillList}

% A more concise alternate 
% \begin{skillList}
%     \doubleItem{Languages:}{Java, C++, Python, C\#, PHP, Prolog, Bash, C, Racket}%
%     {Databases:}{SQL, MongoDB, Neo4j, DynamoDB}
%     \\
%     \doubleItem{Web Development:}{JavaScript, TypeScript, React, HTML/CSS}
%     {Technology:}{Git, AWS, GCP, Azure, Docker, \LaTeX}%
% \end{skillList}
\end{document}